---
output:
  html_document: default
  html_notebook: default
---

```{r}
names(CPI2019)
```
```{r}
CPI2019$pais=CPI2019$Country
CPI2019$Country=NULL
```
```{r}
CPI2019$Score=CPI2019$`CPI score 2019`
CPI2019$`CPI score 2019`=NULL
```
```{r}
CPI2019[,c(1:16)]=NULL

```
```{r}
CPI2019[,c(1:4)]=NULL

```
```{r}
CPI2019$Score=as.numeric(CPI2019$Score)

```
```{r}
str(CPI2019)
```
```{r}
table(CPI2019$Score)
summary(CPI2019$Score)
```
```{r}
CPImodificado=CPI2019

```
```{r,echo=FALSE}
str(CPImodificado)
```
```{r}
names(CPImodificado)
```

```{r}
plot(cars)
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
