```{r}
linkbase="https://en.wikipedia.org/wiki/Democracy_Ranking#:~:text=The%20Democracy%20Ranking%20is%20an%20index%20compiled%20by,produces%20an%20annual%20global%20ranking%20of%20liberal%20democracies."
pathbase='//*[@id="mw-content-text"]/div[1]/table[3]'
library(htmltab)
demorank=htmltab(doc=linkbase,which=pathbase)
```
```{r}
#limpieza
demorank$Country=gsub('Â',"",demorank$Country)
demorank$Rank=NULL
```
```{r}
str(demorank)
```
```{r}
demorank[,-c(1)]=lapply(demorank[,-c(1)], as.numeric)
demorank$Health=NULL
demorank$Environment=NULL
demorank$`Gender Comprehensive`=NULL
```
```{r}
#tendencia central
summary(demorank$`Political System`)
summary(demorank$Economy)
summary(demorank$`Gender Equality`)
summary(demorank$Knowledge)
```
```{r}
hist(demorank$`Political System`)
hist(demorank$Economy)
hist(demorank$`Gender Equality`)
hist(demorank$Knowledge)
```

```{r}
#medidas de dispersion
sd(demorank$`Political System`)
var(demorank$`Political System`)
sd(demorank$Economy)
var(demorank$Economy)
sd(demorank$`Gender Equality`)
var(demorank$`Gender Equality`)
sd(demorank$Knowledge)
var(demorank$Knowledge)

```
```{r}
#estadistica bivariada
#correlaciones
cor.test(~`Political System`+Economy,data=demorank)
cor.test(~`Political System`+Knowledge,data=demorank)
cor.test(~`Political System`+`Gender Equality`,data=demorank)

```
```{r}
cor.test(~Economy+`Political System`,data=demorank)
cor.test(~Economy+Knowledge,data=demorank)
cor.test(~Economy+`Gender Equality`,data=demorank)
```
```{r}
cor.test(~Knowledge+`Political System`,data=demorank)
cor.test(~Knowledge+Economy,data=demorank)
cor.test(~Knowledge+`Gender Equality`,data=demorank)
```
```{r}
cor.test(~`Gender Equality`+`Political System`,data=demorank)
cor.test(~`Gender Equality`+Knowledge,data=demorank)
cor.test(~`Gender Equality`+Economy,data=demorank)
```
```{r}
#graficos de dispersion
plot(`Gender Equality`~Knowledge,data=demorank, main="Diagrama de dispersión",
     xlab="Knowledge", ylab="Gender Equality", pch=20)
```
```{r}
plot(`Political System`~Knowledge,data=demorank, main="Diagrama de dispersión",
     xlab="Knowledge", ylab="Political System", pch=20)
```
```{r}
plot(Economy~Knowledge,data=demorank, main="Diagrama de dispersión",
     xlab="Knowledge", ylab="Economy", pch=20)
```
```{r}
plot(`Political System`~Economy,data=demorank, main="Diagrama de dispersión",
     xlab="Economy", ylab="Political System", pch=20)
```
```{r}
plot(`Gender Equality`~Economy,data=demorank, main="Diagrama de dispersión",
     xlab="Economy", ylab="Gender Equality", pch=20)
```
```{r}
plot(`Gender Equality`~`Political System`,data=demorank, main="Diagrama de dispersión",
     xlab="Political System", ylab="Gender Equality", pch=20)
```

```{r}
plot(cars)
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
